---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## bis620.2023


<!-- badges: start -->
[![R-CMD-check](https://github.com/kaneplusplus/bis620.2023/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kaneplusplus/bis620.2023/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/emarchionni/bis620.2023/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/emarchionni/bis620.2023/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

This is a package that integrates a shiny app for data visualization for the ctrialsgov database that can be found at the [link](https://github.com/presagia-analytics/ctrialsgov). This database includes the history, along with extensive other variables, of the clinical trials conducted worldwide for any type drug since 1995. 

The database is a duckDB database and the package requires its local storage. A function to set the infrastructure and download the database is included in the package.

Along with these main features, the package includes a database on accelerometry data and some function for its visualization in time and frequency domain.

[Here](https://github.com/emarchionni/bis620.2023/actions/workflows/test-coverage.yaml) is a link to the test coverage.

## Installation

You can install the development version of bis620.2023 from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("emarchionni/bis620.2023")
```
<!-- ## Run the shiny app -->

<!-- ```{r} -->
<!-- library(bis620.2023) -->
<!-- download_clinicaltrials() -->
<!-- launch_shiny() -->
<!-- ``` -->


## Example on accel data


This is a basic example which shows you how to solve a common problem:

```{r example}
library(bis620.2023)
accel |> 
  head(100) |> 
  plot_accel()
```



